Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-13 ms/SI.Rmd
add table
update SI

![](../figs/ratio.png){style="display: block; margin: 0 auto" }

@@

@@

Relationships between species mean leaf mass per area (LMA) determined by using whole leaves and leaf discs.
Species groups are divided into four categories on the basis of the medians of the leaf size and leaf thickness across all the species.
Estimates obtained by different leaf punches are plotted separately in different colors.
All the correlations are significant (*P* < 0.001).

![](../figs/sma_grid_col3.png){ width="600" style="display: block; margin: 0 auto" }

>>>>

Relationships between species mean leaf mass per area (LMA) determined by using whole-leaves and leaf discs for species obtained with leaf punches of different diameters.
Dashed lines indicate 1:1 lines.
Blue solid lines indicate standardized major axis (SMA) regressions.
The 95% confidence intervals are resented as the shaded area.
The correlation is significant (*P* < 0.001).

![](../figs/sma_sep.png){ width="400" style="display: block; margin: 0 auto" }

@@

![](../figs/ratio_dm.png){ width="400" style="display: block; margin: 0 auto" }

@@
